### 2018-08-02 ms.tex
Add tmb and R reference.
Add some pop methods.

%Ideal situation is to combine data
benefits of both
%but data are on different scales
%Ewan says there's a relationship.

@@

@@

>>>>

%Ideal situation is to combine data
%benefits of both
%but data are on different scales
%Ewan says there's a relationship.

@@

Raster surfaces of population for the years 2005, 2010 and 2015, were created using a hybrid of data from GPWv4 \cite{gpw4} and WorldPop \cite{tatem2017worldpop}, with the latter taking priority for those pixels where both had population data. 
Final population rasters were created by linear interpolation of the surrounding five-yearly rasters

@@

The models were implemented and fitted using Template Model Builder \cite{TMB} in R \cite{R}
